---
title: "R Notebook"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
install.packages("arules")
install.packages("arulesViz")
install.packages("htmlwidgets")
install.packages("igraph")
install.packages("visNetwork")
library(arules)
library(arulesViz)
library(htmlwidgets)
```

Type any R code in the chunk, for example:
```{r}
data <- read.csv('D:/Projects/r_apriori/Learn-Frequent-Pattern-With-R/uts/budidaya_bandeng_2.csv',sep=",")
trans <- as(data, "transactions")

summary(trans)

```
```{r}
rules <- apriori(
  trans,
  parameter = list(
    supp = 0.3,
    conf = 0.7,
    target = "rules"
  )
)

```
```{r}
inspect(sort(rules, by = "lift"))

```
```{r}

plot_fp <- plot(rules, method = "graph", engine = "htmlwidget")
htmlwidgets::saveWidget(plot_fp, file = "fp_growth_rules.html", selfcontained = TRUE)
```
Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
