---
title: "R Notebook"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
library(ggplot2)
```

Type any R code in the chunk, for example:
```{r}
budidaya.bandeng <- read.csv('D:/Projects/r_apriori/Learn-Frequent-Pattern-With-R/uts/budidaya_bandeng_2.csv',sep=",")
str(budidaya.bandeng)
```
```{r}
plot.bandeng <- ggplot(data = budidaya.bandeng, aes(x=Tahun , y=Volume.Produksi,color=Provinsi))
plot.bandeng + geom_line() + geom_text(aes(label = Volume.Produksi),hjust=-0.2,vjust=-0.5)
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
