---
title: "Analisis Apriori"
author: "Nama Anda"
date: "`r Sys.Date()`"
output: html_document
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}

library(arules)
transactions <- list(
  c("M", "O", "N", "K", "E", "Y"),  # T100
  c("D", "O", "N", "K", "E", "Y"),  # T200
  c("M", "A", "K", "E"),            # T300 (Diperbaiki)
  c("M", "U", "C", "K", "Y"),       # T400
  c("C", "O", "K", "I", "E")        # T500
)

trans <- as(transactions, "transactions")
inspect(trans)
```

Type any R code in the chunk, for example:
```{r}
trans
```
```{r}
freq1 <- eclat(trans, parameter = list(support = 0.5, target = "frequent itemsets"))
inspect(freq1)
```
```{r}
freq2 <- eclat(trans)
freq2
```
```{r}
inspect(freq2)
```
```{r}
rules <- ruleInduction(freq1, confidence = .8)
rules
```
```{r}
inspect(sort(rules, by = 'lift'))
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
